Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | AI & digital&nbsp;humanities&nbsp;instructor </font>

### 2023-07-22 index.Rmd
news

- Hosted students at the CUDAN lab via the job shadowing (töövari) programme of the Estonian Tagasi Kooli programme (online April 2021, live in November 2020).
- I helped my supervisor Prof. Kenny Smith carry out a number of linguistics workshops in primary schools around Edinburgh and Lothian, in school years 2018/2019 and 2019/2020.
- Entered [a video](https://www.youtube.com/watch?v=t8InfFEIINc) to Science Magazine's 11th [Dance Your Ph.D contest](https://www.sciencemag.org/projects/dance-your-phd). The idea is to explain your research topic to the general public though interpretive dance. We didn't win but it was a fun one to do!
- Co-organized the bimonthly [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/) during 2016-2018. 
- Co-organized the [Linguistics and English Language Postgraduate Conference](http://www.lel.ed.ac.uk/~pgc/) of 2017 in Edinburgh, the [Why Linguistics Conference](http://whylinguistics.ut.ee) (2015) and the [Graduate Conference on Areal Linguistics, Grammar and Contacts](http://arealling.ut.ee) (2012) in Tartu, Estonia.

>>>>

- Wrote an opinion piece in ERR [Novaator](https://novaator.err.ee/1609007981/andres-karjus-tehisintellekt-seab-juba-sel-sugisel-koolid-sundvaliku-ette) on how generative AI will affect education in the near future (16.06.2023)
- Gave a number of interviews on artificial intelligence topics in Spring 2023 (in Estonian): [Äripäev radio](https://www.aripaev.ee/saated/2023/03/30/tehisintellekt-muudab-taiskasvanute-oppimist-ja-opikogemust), [TÜHI Eeter podcast](https://www.levila.ee/raadio/tuhi-eeter/kumb-on-arukam-kas-inimaru-voi-tehisaru), [PostimeesTV](https://haridus.postimees.ee/7722633/ekspert-eetris-andres-karjus-kas-chatgpt-hakkab-mojutama-meie-vaartusi-ja-kaitumist), BFM [Luna TV](https://www.youtube.com/watch?v=cXpNkDgfP7Y),  [Postimees](https://www.postimees.ee/7717736/tehisintellekti-abil-kodutoo-kirjutajaid-on-pea-voimatu-vahele-votta)
- News piece in [Pealinn](https://pealinn.ee/2022/09/29/vaata-millised-ettevotjad-saavad-tanavu-tunnustamise-osaliseks-ja-voidavad-auhinna/) on Tallinn city enterpreneurship prizes 2022, including me & colleagues for our media monitoring AI prototype in collaboration with AS Ekspress Grupp.
- Hosted students at the CUDAN lab via the job shadowing (töövari) programme of the Estonian Tagasi Kooli programme (online April 2021, live in November 2020).
- I helped my supervisor Prof. Kenny Smith carry out a number of linguistics workshops in primary schools around Edinburgh and Lothian, in school years 2018/2019 and 2019/2020.
- Entered [a video](https://www.youtube.com/watch?v=t8InfFEIINc) to Science Magazine's 11th [Dance Your Ph.D contest](https://www.sciencemag.org/projects/dance-your-phd). The idea is to explain your research topic to the general public though interpretive dance. We didn't win but it was a fun one to do!
- Co-organized the bimonthly [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/) during 2016-2018. 
- Co-organized the [Linguistics and English Language Postgraduate Conference](http://www.lel.ed.ac.uk/~pgc/) of 2017 in Edinburgh, the [Why Linguistics Conference](http://whylinguistics.ut.ee) (2015) and the [Graduate Conference on Areal Linguistics, Grammar and Contacts](http://arealling.ut.ee) (2012) in Tartu, Estonia.

### 2023-07-22 news.Rmd
news

>>>>

- Out now in Frontiers Neuroscience: Yilmaz, Lotman, Karjus, Tikka, "An embodiment of the cinematographer: emotional and perceptual responses to different camera movement techniques" | [open access](https://doi.org/10.3389/fnins.2023.1160843) (03.07.2023)

- Out now in EPJDS: Karjus et al., "Compression ensembles quantify aesthetic complexity and the evolution of visual art" | [open access](https://doi.org/10.1140/epjds/s13688-023-00397-3) | [code](https://github.com/andreskarjus/compression_ensembles) (14.06.2023)

- Published an opinion piece in the popular science outlet [Novaator](https://novaator.err.ee/1609007981/andres-karjus-tehisintellekt-seab-juba-sel-sugisel-koolid-sundvaliku-ette) on how generative AI will affect education in the near future (16.06.2023)

- New preprints: Ohm et al. "Collection Space Navigator: An Interactive Visualization Interface for Multidimensional Datasets", and Zemaityte et al. "Quantifying the global film festival circuit: Networks, diversity, and public value creation"

- Spring 2023: Been doing more workshops at multiple Estonian higher education institutions, schools and companies on generative AI, text and image generators; several workshops and public speaking engagements coming up; more info at [datafigure.eu]((https://datafigure.eu)
